Application-Level Regression Testing Framework using Jenkins

### 2017-03-20 manuscript/manuscript.tex
wrapped an extended line a bit

 # -- The following sets OTP for Jenkins SSL connection
  DefineExternalAuth pwauth+session pipe /usr/local/bin/
  pwauth+session
  <LocationMatch / > 
    AuthType Basic
    AuthBasicProvider external
    AuthName "NCSA RSA OTP login" 
    AuthExternal pwauth+session
    require valid-user

@@

 /usr/local/bin/pwauth+session: https://github.com/reubendb/
 BasicAuthOTPSession/blob/master/BasicAuthOTPSession.py#L1
\end{lstlisting}
\subsection{LDAP with Jenkins}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore

>>>>

 # -- OTP for Jenkins SSL connection
   DefineExternalAuth pwauth+session pipe 
   /usr/local/bin/pwauth+session
  <LocationMatch / > 
    AuthType Basic
    AuthBasicProvider external
    AuthName "NCSA RSA OTP login" 
    AuthExternal pwauth+session
    require valid-user

@@

 /usr/local/bin/pwauth+session: 
 https://github.com/reubendb/BasicAuthOTPSession
 /blob/master/BasicAuthOTPSession.py#L1
\end{lstlisting}
\subsection{LDAP with Jenkins}
\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{LDAP-Jenkins}
\caption{ Use LDAP with Jenkins }
\label{fig:LDAP-Jenkins}
\end{figure}
To enable LDAP, the LDAP Plugin was installed. To configure, from the console view, select Manage Jenkins, then select Configure Global Security. In the Security Realm section select the Advanced... tab. Input your LDAP server name and root DN. Click the Test Button.\\
\\
My first stab at this failed as an anonymous connection to our LDAP because we are using a local CA.
WARNING: Failed to search LDAP for username, 
sun.security.provider.certpath.SunCertPathBuilderException:
unable to find valid certification path to requested target\\
\\
We had to add our certificate to the keystore:
/usr/java/default/jre/bin/keytool -list -keystore cacerts -imle /etc/openldap/cacerts/cacert.pem
Enter keystore password: Trust this certificate? [no]:  yes\\
Certificate was added to keystore
